Analyzing Trends in U.S. Residential Real Estate Prices

### 2024-04-17 outputs/paper/paper.qmd
paper final draft

The Root Mean Square Error (RMSE) of the GAM is lower than that of the multiple regression but higher than that observed in the polynomial regression, indicating that the model's predictions are reasonably accurate, yet there may be some potential for enhancement. This metric confirms that the GAM has improved the predictive capability of the model, providing an accuracy that is comparable, but not necessarily superior, to the polynomial approach. This performance might reflect the complexities and variabilities inherent in the housing market data, which can challenge even sophisticated models like the GAM.

@@

The choice between these models should be informed by the balance between the need for simplicity and the desire to capture complex data relationships. While the Polynomial Regression strikes a balance, offering a good fit without overly complicating the model, the GAM provides the most flexibility, which could be crucial for analyzing more intricate datasets or where the precise nature of relationships between variables is less understood.

@@

Economically, this trend could boost industries related to home construction, renovation, and furnishing as consumers seek to enhance or acquire properties that match their new preferences. However, it also calls for a careful evaluation of the environmental impacts, as larger homes generally require more resources and energy, posing challenges to sustainability goals [@citeUKPollution]. This balance between accommodating consumer preferences and maintaining sustainability will be crucial for future policy and economic strategies in the housing sector.

@@

While this study is detailed, there is room for further enhancement and expansion. Future research should incorporate additional economic variables, such as interest rates and housing supply data, to offer a more comprehensive understanding of the market forces involved. Longitudinal studies that examine the effects of policy changes over time could also enrich our understanding of market dynamics. Advances in data collection technology could enable real-time analysis of market trends, allowing for a more responsive approach to rapid changes in the market. Additionally, broadening the scope to include rental markets and affordable housing would provide insights into the entire housing spectrum, crucial for developing holistic housing strategies that benefit all societal segments.

>>>>

The Root Mean Square Error (RMSE) of the GAM is lower than that of the multiple regression but higher than that observed in the polynomial regression, indicating that the model's predictions are reasonably accurate, yet there may be some potential for enhancement. This metric confirms that the GAM has improved the predictive capability of the model, providing an accuracy that is comparable, but not necessarily superior, to the polynomial approach. This performance might reflect the complexities and variabilities inherent in the housing market data, which can challenge even complex models like the GAM.

@@

The choice between these models should be informed by the balance between the need for simplicity and the desire to capture complex data relationships. While the Polynomial Regression strikes a balance, offering a good fit without overly complicating the model, the GAM provides the most flexibility, which could be important for analyzing more intricate datasets or where the precise nature of relationships between variables is less understood.

@@

Economically, this trend could boost industries related to home construction, renovation, and furnishing as consumers seek to enhance or acquire properties that match their new preferences. However, it also calls for a careful evaluation of the environmental impacts, as larger homes generally require more resources and energy, posing challenges to sustainability goals [@citeUKPollution]. This balance between accommodating consumer preferences and maintaining sustainability will be important  for future policy and economic strategies in the housing sector.

@@

While this study is detailed, there is room for further enhancement and expansion. Future research should incorporate additional economic variables, such as interest rates and housing supply data, to offer a better understanding of the market forces involved. Longitudinal studies that examine the effects of policy changes over time could also enrich our understanding of market dynamics. Advances in data collection technology could enable real-time analysis of market trends, allowing for a more responsive approach to rapid changes in the market. Additionally, broadening the scope to include rental markets and affordable housing would provide insights into the entire housing spectrum, important for developing holistic housing strategies that benefit all societal segments.
